### 2021-03-31 README.Rmd
update readme

> Marwick, B and P. Smith, (2021). `r Title`. _Big Data and Society_ <https://doi.org/xxx/xxx>

@@

> Marwick, B and P. Smith, (2021). `r Title`.  Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.31235/osf.io/7gvza>

@@

> Marwick, B and P. Smith, (`r format(Sys.Date(), "%Y")`). Compendium of R code and data for `r Title`. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.17605/OSF.IO/AY27G>

@@

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
remotes::install_github("benmarwick/worldheritagewikipedia")
```

>>>>

> Marwick, B.[![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0001-7879-4531) and P. Smith, (2021). `r Title`. _Big Data and Society_ <https://doi.org/xxx/xxx>

@@

> Marwick, B.[![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0001-7879-4531) and P. Smith, (2021). `r Title`.  Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.31235/osf.io/7gvza>

@@

> Marwick, B.[![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0001-7879-4531) and P. Smith, (`r format(Sys.Date(), "%Y")`). Compendium of R code and data for `r Title`. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.17605/OSF.IO/AY27G>

@@

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("benmarwick/worldheritagewikipedia")
```
